---
title: "First Homework"
author: "Anran Shao"
Date: "2019/9/19" 
output: github_document 
---

# Set up
```{r set up,include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

# Problem 1 

## Creating a data frame and getting the mean of each variables
```{r}
dataframe1 = tibble(
  vec_numeric = rnorm(8),
  vec_logical = vec_numeric > 0,
  vec_character = c("mouse","pig","dog","cow","rabbit","sheep","bird","penguin"),
  vec_factor = c("pink","white","white","pink","blue","blue","pink","white"),
  )
class(pull(dataframe1,vec_numeric))
class(pull(dataframe1,vec_logical))
class(pull(dataframe1,vec_character))

mean(dataframe1$vec_numeric)
mean(dataframe1$vec_logical)
mean(dataframe1$vec_factor)
mean(dataframe1$vec_character)
```
** The means for numeric variable and logical vector are workable, but factor and character vectors are not workable because they are not numeric. 

## Multiplication of two variables
```{r eval=FALSE}
set.seed(1)
logical_num = as.numeric(dataframe1$vec_logical)
logical_fac = as.factor(dataframe1$vec_logical)
logical_fac_num = as.numeric(as.factor(dataframe1$vec_logical))

logical_num  * dataframe1$vec_numeric
logical_fac * dataframe1$vec_numeric
logical_fac_num * dataframe1$vec_numeric
```
The multiplication is not meaningful for factor

# Problem2 -- the use of inline R code, plotting, and the behavior of ggplot for variables of different types.
## Creating a data frame
```{r}
set.seed(1)

plot_df = tibble(
  x = rnorm(500),
  y = rnorm(500),
  vec_logical = x + y > 1,
  vec_numeric = as.numeric(vec_logical),
  vec_factor = as.factor(vec_logical),
)
```
Short Description: 
The size of the dataset is `r nrow(plot_df)` and `r ncol(plot_df)`.
The mean, median, and the standard deviation of `r mean(pull(plot_df,x))`.
The proportion of cases for which `r mean(pull(plot_df, vec_logical) == "TRUE")`.
